\section{Teach Yourself Haskell in 21 Days - LOL}

Teach Yourself Haskell in 21 Days - LOL.

LolLol LolLol Lol LolLolLolLolLol Lol Lol (\emph{LOL}, \emph{ROLF}, \emph{LOL}, \emph{ROLF}). Teach Yourself Haskell in 21 Days - LOL

Teach Yourself Haskell in 21 Days - LOL.  Haskell in 21 Days - LOL. Teach Yourself Haskell in 21 Days - LOL. Teach Yourself Haskell in 21 Days - LOL. Teach Yourself Haskell in 21 Days - LOL. Teach Yourself Haskell in 21 Days - LOL.  Haskell in 21 Days - LOL. Learn You Haskell in 21 days - LOL. Learn You Haskell in 21 days - LOL. Learn You Haskell in 21 days - LOL. Learn You Haskell in 21 days - LOL. Learn You Haskell in 21 days - LOL.

Teach Yourself Haskell in 21 Days - LOL. Teach Yourself Haskell in 21 Days - LOL. Teach Yourself Haskell in 21 Days - LOL. Teach Yourself Haskell in 21 Days - LOL. Teach Yourself Haskell in 21 Days - LOL. Teach Yourself Haskell in 21 Days - LOL. Teach Yourself Haskell in 21 Days - LOL. Teach Yourself Haskell in 21 Days - LOL. Teach Yourself Haskell in 21 Days - LOL. Teach Yourself Haskell in 21 Days - LOL. Teach Yourself Haskell in 21 Days - LOL.

LOL LOL LOL LOL LOL LOL LOL LOL \emph{ROLF LOL} LOL LOL LOL LOL LOL LOL LOL.

\begin{verbatim}
--  Haskell in 21 Days - LOL
data Lol = Lmao | Rolf Lol Lol

instance Monoid Lol where
    mempty = Lmao
    mappend = Rolf

\end{verbatim}

Teach Yourself Haskell in 21 Days - LOL (\texttt{Lol} Teach Yourself Haskell in 21 Days - LOL). Teach Yourself Haskell in 21 Days - LOL. Teach Yourself Haskell in 21 Days - LOL. Teach Yourself Haskell in 21 Days - LOL.Teach Yourself Haskell in 21 Days - LOL. Teach Yourself Haskell in 21 Days - LOL.

\subsection{Teach Yourself Haskell in 21 Days - ROLF}

Teach Yourself Haskell in 21 Days - LOOOOOL. Teach Yourself Haskell in 21 Days - LOL. Teach Yourself Haskell in 21 Days - LOL. Teach Yourself Haskell in 21 Days - LOL.. Teach Yourself Haskell in 21 Days - LOL.

Teach Yourself Haskell in 21 Days - LOL.Teach Yourself Haskell in 21 Days - LOL. Teach Yourself Haskell in 21 Days - LOL. Teach Yourself Haskell in 21 Days - LOL.
